---
title: "playing_with_data"
author: "Franky"
date: '2023-11-20'
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("/Users/frankyzhang/Desktop/Ofer-s-Proj")
library(readxl)
library(tidyverse)
library(ggplot2)
```


## 1. From LEQ --> dose

### 1.1 verification of cumulatiive dose calculation (data source: Dosimeter sample raw data and notes.xlsx)

$$Dose = 100 \times \frac{T}{T_c} \times 2^{(L - L_c)/Q}$$
```{r}
Dosimeter.sample <- read_excel("Dosimeter sample raw data and notes.xlsx", sheet = 2)
# criterion here to use:
# Lc <- 85
# Tc <- 8

dose_per <- function(Time, Leq, Lc = 85, Tc = 8, Q = 3){
  return(100*(Time/Tc)*2^((Leq - Lc)/Q))
}
# verify the calculation of sample
SampleDose.cum <- 0
time.seq <- Dosimeter.sample$`Time H`
leq.seq  <- Dosimeter.sample$`LEQ dB`
for(i in 1:(nrow(Dosimeter.sample)-1)){
  SampleDose.cum = SampleDose.cum + dose_per(Time = (time.seq[i+1] - time.seq[i]), Leq = leq.seq[i+1])
}
print(SampleDose.cum)
rm(time.seq, leq.seq)
```


### 1.2 verification of daily dose calculation (data source: DosimetryData_Example.xlsx$OriginalOutput)

```{r}
OriginalOutput <- read_excel("DosimetryData_Example.xlsx", sheet = 2)
hours.map <- OriginalOutput[c("Day1_totalhrs", "Day2_totalhrs", "Day3_totalhrs", "Day4_totalhrs", 
                              "Day5_totalhrs", "Day6_totalhrs", "Day7_totalhrs", "Day8_totalhrs")]
lep.map   <- OriginalOutput[c("Day1_LEQ", "Day2_LEQ", "Day3_LEQ", "Day4_LEQ", 
                              "Day5_LEQ", "Day6_LEQ", "Day7_LEQ", "Day8_LEQ")]
dailydose.check <- OriginalOutput[c("Day1_Dose", "Day2_Dose", "Day3_Dose", "Day4_Dose", 
                                    "Day5_Dose", "Day6_Dose", "Day7_Dose", "Day8_Dose")]
columns <- c()
for (i in 1:ncol(hours.map)) {columns[i]  = paste("Day", i, "_Dose", sep = "")}

dailydose.cal <- data.frame(matrix(ncol = ncol(hours.map), nrow = nrow(hours.map)))
colnames(dailydose.cal) <- columns

for(i in 1:nrow(hours.map)){
  for(j in 1:ncol(hours.map)){
    dailydose.cal[i, j] = dose_per(Time = hours.map[i, j], Leq = lep.map[i, j])
  }
}
# round(dailydose.cal, 2)
# dailydose.cal
# dailydose.check
```

_Conclusion:_

Until now, this step is good, which means the calculation way from LEQ(any time interval) to 8-hour-criterion dose is reliable. 




## 2. From 3.75 minutes Leq --> daily Leq (data source: DosimetryData_Example.xlsx$LA_matrix & $DayOfWeek)

### 2.1 Data loading and processing

```{r}
# load .xlsx file and identify na with "NaN"
LA_matrix <- read_excel("DosimetryData_Example.xlsx", sheet = 4, col_names = TRUE, na = "NaN")
# New names:
# • `MC16_17, 11-18-16` -> `MC16_17, 11-18-16...67`
# • `MC16_17, 11-18-16` -> `MC16_17, 11-18-16...68`
DayOfWeek <- read_excel("DosimetryData_Example.xlsx", sheet = 6, col_names = TRUE, na = "NaN")
# New names:
# • `MC16_17, 11-18-16` -> `MC16_17, 11-18-16...67`
# • `MC16_17, 11-18-16` -> `MC16_17, 11-18-16...68`

# indicting that contains duplicated names
LA_matrix <- LA_matrix %>% select(-c(`MC16_17, 11-18-16...68`))
colnames(LA_matrix)[colnames(LA_matrix) == "MC16_17, 11-18-16...67"] <- "MC16_17, 11-18-16"
DayOfWeek <- DayOfWeek %>% select(-c(`MC16_17, 11-18-16...68`))
colnames(DayOfWeek)[colnames(DayOfWeek) == "MC16_17, 11-18-16...67"] <- "MC16_17, 11-18-16"

Week.Index <- data.frame(matrix(ncol = ncol(DayOfWeek), nrow = nrow(DayOfWeek)))
colnames(Week.Index) = colnames(DayOfWeek)

for(j in 1:ncol(DayOfWeek)){
  week_index = 1
  Week.Index[1, j] = 1
  for(i in 2:nrow(DayOfWeek)){
    week_index = ifelse(DayOfWeek[i-1,j] - DayOfWeek[i,j] > 1, week_index+1,  week_index) # identify the change of week
    Week.Index[i, j] = week_index
  }
}

# combine the Week.Index and DayOfWeek 
MWeek.Index <- as.matrix(Week.Index)
MDayOfWeek  <- as.matrix(DayOfWeek)
Day.Index <- matrix(paste(MWeek.Index, MDayOfWeek, sep="-"), nrow=nrow(MWeek.Index), 
                    dimnames=dimnames(MWeek.Index)) %>% as.data.frame()
# Day.Index$CT16_01[549] # looks good 

# table(Day.Index$CT16_01)
#   1-6   1-7   2-1   2-2   2-3   2-4   2-5   2-6  2-NA NA-NA 
#   164   384   384   384   384   384   384   208     1    11 
# 164*0.0625 # =10.25 
# which is the same as $OriginalOutput

# create list to store every student's data 
LA.Seq <- list()
for (i in 1:length(colnames(LA_matrix))) {
  # "CT16_01" 
  # "MC16_17, 11-18-16"
  LA.Seq[[i]] <- data.frame(Day.Index[colnames(LA_matrix)[i]], 
                            LA_matrix[colnames(LA_matrix)[i]])
  colnames(LA.Seq[[i]]) <- c("Week-Day", "Leq(3.75min)")
}
# rename the list
names(LA.Seq) <- colnames(LA_matrix)
LA.names <- names(LA.Seq)

# remove NA records
for(key in LA.names){
  LA.Seq[[key]] = LA.Seq[[key]] %>% filter(!grepl("NA", `Leq(3.75min)`))
  LA.Seq[[key]] = LA.Seq[[key]] %>% filter(!grepl("NA", `Week-Day`))
}

# remove terms that no longer use
rm(MDayOfWeek, MWeek.Index, Week.Index, DayOfWeek)

# table(LA.Seq[["CT16_01"]]["Week-Day"]) * 0.0625
#   1-6   1-7   2-1   2-2   2-3   2-4   2-5   2-6 
# 10.25 24.00 24.00 24.00 24.00 24.00 24.00 13.00 
# table(LA.Seq[["CT16_02, 4-15-16"]]["Week-Day"]) * 0.0625
# Week-Day
#     1-5     1-6     1-7     2-1     2-2     2-3     2-4     2-5 
# 10.6875 24.0000 24.0000 24.0000 24.0000 24.0000 24.0000 13.3125 

# perfect with OriginalOutput
```

### 2.2 Leq for each day calculation 

$$L_{Aeq,T} = 10 * \log_{10}(\frac{1}{T_{duration}} * \sum_{i = 1}^{n}t_i * 10^{\frac{L_i}{10}})$$
```{r}
DayLeq <- list()
for(key in LA.names){
  # key = "CT16_01"
  df <- LA.Seq[[key]]
  for(day in unique(df$`Week-Day`)){
    # day = "1-6"
    sub_df <- df %>% filter(`Week-Day` == day)
    exp_sum <- 0
    Time_dur <- nrow(sub_df) * 0.0625
    ti <- 0.0625
    exp_sum <- 0
    for(i in 1:nrow(sub_df)){
      exp_sum <- exp_sum + (1/Time_dur)*ti*10^(sub_df[i, 2]/10)
    }
    DayLeq[[key]][day] <- 10 * log(exp_sum, base = 10)
  }
}
LA.Seq[["CT16_01"]] %>% filter(`Week-Day` == "1-6") 
DayLeq[["CT16_01"]]
```


### 1.3 compare the daily dose via "Daily Leq" and "Cumulative (3.75 min) Leq"

```{r}
# For each student, calculate cumulative dose for every single day 
cumdose.cal <- list()
for(key in LA.names){
  # cat("key ready")
  df <- LA.Seq[[key]]
  days <- unique(LA.Seq[[key]]$`Week-Day`)
  index = 1
  for(day in days){
    # cat("day ready\n")
    sub_df <- df %>% filter(`Week-Day` == day)
    # cat("sub_df ready\n")
    Dose.cum <- c()
    Dose.cum[1] = 0
    for(i in 1:(nrow(sub_df)-1)){
      Dose.cum[i+1] = Dose.cum[i] + dose_per(Time = 0.0625, Leq = sub_df$`Leq(3.75min)`[i+1])
    }
    cumdose.cal[[key]][index] = tail(Dose.cum, 1)
    index = index + 1
  }
}
# cumdose.cal[["CT16_01"]]

cumdose.cal.df <- data.frame(matrix(ncol = ncol(dailydose.cal), nrow = nrow(dailydose.cal) - 1))
colnames(cumdose.cal.df) <- colnames(dailydose.cal)
for(i in 1:length(LA.names)){
  vec <- cumdose.cal[[i]]
  for(j in 1:length(vec)){
    cumdose.cal.df[i, j] = vec[j]
  }
}

dose.cal.diff <- dailydose.cal[-67, ] - cumdose.cal.df
print(round(dose.cal.diff, 2)[sample(1:79, 10), ])
```
_Conclusion_

The maximum difference is around 20% dose for each day. Majority of them are < 1%. Using dayily Leq to estimate rather then calculate cumulations is reliable on the whole. 




## Looking into the missing data in the Sequence 

```{r}
MissingCheck <- data.frame(matrix(nrow = 3, ncol = ncol(LA_matrix)))
colnames(MissingCheck) = colnames(LA_matrix)

for(i in 1:length(colnames(LA_matrix))){
  # i = 1
  vec = as.matrix(LA_matrix)[, i]
  vec[vec > 0] = 1
  
  count = table(vec)
  MissingCheck[1, i] = count[1]
  MissingCheck[2, i] = count[2]
  MissingCheck[3, i] = nrow(LA_matrix) - (count[1] + count[2])
}
LA_MissingCheck <- round(MissingCheck/2688, 2)
rownames(LA_MissingCheck) <- c("== 0", "!= 0", "NA")
apply(LA_MissingCheck, 1, mean)

#   == 0       != 0         NA 
# 0.67886076 0.27848101 0.04240506 

# 67.8% data are 0, which means not captured by the Dosimeter
```


